Local-to-Global Mariculture Modelling

### 2025-12-11 docs-working/01_tidying_data.qmd
Moving files around

---
title: "Tidying data"
author: Richard Cottrell
date: today
editor: source
---

```{r setup}
library(tidyverse)
library(here)
library(terra)
library(qs)
library(magrittr)

>>>>

---
title: "Tidying data"
author: Richard Cottrell
date: today
execute:
  eval: false
---

```{r setup, include=F, cache=F}
library(tidyverse)
library(here)
library(terra)
library(qs)
library(magrittr)
library(purrr)

### 2025-12-11 docs-working/02_extracting_production_locations.qmd
Moving files around

```{r setup}
library(tidyr)
library(dplyr)
library(magrittr)
library(here)
library(janitor)
library(sf)
library(qs)
library(countrycode)
library(terra)
library(units)
library(readr)
library(ggplot2)

@@

```{r clean-raw-data}
# Get aquaculture quantity in tonnes live weight
quantity <- file.path(rawdata_path, "Aquaculture_2025.1.0", "Aquaculture_Quantity.csv") %>% 
  read.csv() %>% 
  clean_names() %>% 
  mutate(value = set_units(value, "t")) %>% 
  select(-measure)

# Apply environment codes and filter by "marine"
environment_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_PRODENVIRONMENT.csv") %>% 
  read.csv() %>% 
  distinct(Code, Name_En)

@@

# Apply species codes
species_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SPECIES_GROUPS.csv") %>% 
  read.csv() %>% 
  distinct(X3A_Code, Scientific_Name)

@@

# Apply status codes
status_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_SYMBOL_SDMX.csv") %>% 
  read.csv() %>% 
  distinct(Symbol, Name_En, Description_En)

@@

# Apply country and area codes
country_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_COUNTRY_GROUPS.csv") %>% 
  read.csv() %>% 
  select(UN_Code, Identifier, Name_En, ISO3_Code)
area_codes <- file.path(rawdata_path, "Aquaculture_2025.1.0", "CL_FI_WATERAREA_GROUPS.csv") %>% 
  read.csv() %>% 
  select(Code, Name_En)

>>>>

```{r setup, include=F, cache=F}
library(tidyr)
library(dplyr)
library(magrittr)
library(here)
library(janitor)
library(sf)
library(qs)
library(countrycode)
library(terra)
library(units)
library(readr)
library(ggplot2)
library(purrr)

@@

```{r clean-raw-data}
# Get aquaculture quantity in tonnes live weight
quantity <- file.path(bigdata_path, "Aquaculture_2025.1.0", "Aquaculture_Quantity.csv") %>% 
  read.csv() %>% 
  clean_names() %>% 
  mutate(value = set_units(value, "t")) %>% 
  select(-measure)

# Apply environment codes and filter by "marine"
environment_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_PRODENVIRONMENT.csv") %>% 
  read.csv() %>% 
  distinct(Code, Name_En)

@@

# Apply species codes
species_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_SPECIES_GROUPS.csv") %>% 
  read.csv() %>% 
  distinct(X3A_Code, Scientific_Name)

@@

# Apply status codes
status_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_SYMBOL_SDMX.csv") %>% 
  read.csv() %>% 
  distinct(Symbol, Name_En, Description_En)

@@

# Apply country and area codes
country_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_COUNTRY_GROUPS.csv") %>% 
  read.csv() %>% 
  select(UN_Code, Identifier, Name_En, ISO3_Code)
area_codes <- file.path(bigdata_path, "Aquaculture_2025.1.0", "CL_FI_WATERAREA_GROUPS.csv") %>% 
  read.csv() %>% 
  select(Code, Name_En)

### 2025-12-11 docs-working/05_formulating_feeds.qmd
Moving files around

```{r setup}
#| code-summary: R setup

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% purrr::walk(source)
```

@@

There is no check or correction here to ensure that protein + lipid + ash + carb = 1 in the incoming data. This was checked manually prior to import.

@@

@@

feed_inputs <- file.path(input_feed_profile_path, "all_feeds.xlsx") %>% 
  read_excel(sheet = "all_feeds") %>% 
  rename(novel_inclusive_1 = novel_inclusive)
feed_inputs$novel_inclusive_2 <- feed_inputs$novel_inclusive_1 # same composition

feed_inputs <- feed_inputs %>% 
  pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "category"))) %>% 
  mutate(
    feed = as.factor(feed),
    ingredient = as.factor(ingredient),
    proportion = case_when(is.na(proportion) ~ 0, T ~ proportion)
  ) %>% 
  left_join(ingreds, by = "ingredient") %>% 
  select(-prop_P, -P_digestibility)

# Novel feeds use the minimum and maximum digestibility values
feed_inputs <- feed_inputs %>% 
  mutate(
    protein_digestibility = case_when(
      feed == "novel_inclusive_1" & !is.na(max_protein_digestibility) ~ max_protein_digestibility,
      feed == "novel_inclusive_2" & !is.na(min_protein_digestibility) ~ min_protein_digestibility,
      T ~ mean_protein_digestibility,
    ),
    carb_digestibility = case_when(
      feed == "novel_inclusive_1" & !is.na(max_carb_digestibility) ~ max_carb_digestibility,
      feed == "novel_inclusive_2" & !is.na(min_carb_digestibility) ~ min_carb_digestibility,
      T ~ mean_carb_digestibility,
    ),
    lipid_digestibility = case_when(
      feed == "novel_inclusive_1" & !is.na(max_lipid_digestibility) ~ max_lipid_digestibility,
      feed == "novel_inclusive_2" & !is.na(min_lipid_digestibility) ~ min_lipid_digestibility,
      T ~ mean_lipid_digestibility,
    )
  ) %>% 
  select(-contains(c("min", "max", "mean")))

@@

@@

```{r formulate feeds}
#| code-summary: Format feeds as lists to feed into targets

feed_params <- purrr::map(feed_types, function(ft) {
  df <- feed_inputs %>% 
    filter(feed == ft) 
  list(
    Proteins = df %>% 
      select(ingredient, proportion, contains("protein")) %>% 
      rename(macro = protein, digest = protein_digestibility),
    Carbohydrates = df %>% 
      select(ingredient, proportion, contains("carb")) %>% 
      rename(macro = carb, digest = carb_digestibility),
    Lipids = df %>% 
      select(ingredient, proportion, contains("lipid")) %>% 
      rename(macro = lipid, digest = lipid_digestibility)
  )
}) %>% 
  setNames(feed_types)
```

```{r save}
qsave(feed_params, file.path(output_species_data_path, "feed_params.qs"))
```

# Similarity

For later - how similar are the diets?

```{r}
#| label: diet-similarity

feed_simil <- feed_inputs %>% 
  select(ingredient, feed, proportion) %>% 
  as.data.frame() %>% 
  pivot_wider(
    names_from = feed,
    values_from = proportion,
    id_cols = ingredient,
    values_fn = as.numeric
  ) %>% 
  mutate(
    diff_PD_MD = abs(marine_dominant - plant_dominant),
    diff_PD_NI = abs(novel_inclusive - plant_dominant)
  )

1 - sum(feed_simil$diff_PD_MD, na.rm = T)
1 - sum(feed_simil$diff_PD_NI, na.rm = T)
```

```{r}

```

>>>>

```{r setup, include=F, cache=F}
#| code-summary: R setup

library(arrow)
library(sf)
library(dplyr)
library(tidyr)
library(terra)
library(magrittr)
library(purrr)
library(furrr)
library(future)
library(tictoc)
library(ggplot2)
library(fs)
library(conflicted)
library(stringr)
library(readxl)
library(units)
library(qs)
library(here)
conflicts_prefer(dplyr::filter(), dplyr::select(), .quiet = T)

here("src") %>% list.files(pattern = "\\.R$", full.names = TRUE) %>% walk(source)
```

@@

There is no check or correction here to ensure that protein + lipid + ash + carb = 1 in the incoming ingredient data. This was checked manually prior to import.

@@

Unlike ingredients, the feeds do not need to be checked for sum = 1 prior to import. That check is done here.

@@

feed_inputs <- file.path(input_feed_profile_path, "all_feeds.xlsx") %>% 
  read_excel(sheet = "all_feeds")

feed_inputs <- feed_inputs %>% 
  pivot_longer(names_to = "feed", values_to = "proportion", cols = !contains(c("ingredient", "category"))) %>% 
  mutate(
    feed = as.factor(feed),
    ingredient = as.factor(ingredient),
    proportion = case_when(is.na(proportion) ~ 0, T ~ proportion)
  ) %>% 
  left_join(ingreds, by = "ingredient")
```

Include the range of digestibility values so that feeds can be sampled (if required) within the targets pipeline.

```{r min-max-values}
#| code-summary: Novel feeds use the mean digestibility values

feed_inputs <- feed_inputs %>% 
  rename(
    protein_digestibility = mean_protein_digestibility,
    carb_digestibility = mean_carb_digestibility,
    lipid_digestibility = mean_lipid_digestibility
  )

@@

# Prepare for pipeline

@@

```{r formulate-feeds}
#| code-summary: Format feeds as lists to feed into targets

feed_types <- levels(feed_inputs$feed)

feed_params <- purrr::map(feed_types, function(ft) {
  # Filter by specified feed
  df <- feed_inputs %>% filter(feed == ft)

  list(
    Proteins = df %>% 
      select(ingredient, proportion, contains("protein")) %>% 
      rename(
        macro = protein, 
        digest = protein_digestibility,
        min_digest = min_protein_digestibility,
        max_digest = max_protein_digestibility
      ),
    Carbohydrates = df %>% 
      select(ingredient, proportion, contains("carb")) %>% 
      rename(
        macro = carb, 
        digest = carb_digestibility,
        min_digest = min_carb_digestibility,
        max_digest = max_carb_digestibility
      ),
    Lipids = df %>% 
      select(ingredient, proportion, contains("lipid")) %>% 
      rename(
        macro = lipid, 
        digest = lipid_digestibility,
        min_digest = min_lipid_digestibility,
        max_digest = max_lipid_digestibility
      )
  )
}) %>% 
  setNames(feed_types)
```

```{r save}
#| code-summary: Save feed params file

qsave(feed_params, file.path(output_species_data_path, "feed_params.qs"))
```

### 2025-12-11 docs-working/06_run_atlantic_salmon_model.qmd
Moving files around

```{r}
#| label: setup
#| warning: false
#| message: false

@@

```{r}
#| label: filenames

# Set up parallel processing
# plan(multisession, workers = parallelly::availableCores()-1)

@@

Load and process farm coordinate data with appropriate timing parameters for Northern and Southern hemisphere farms.

```{r}
#| label: farm-coordinates

@@

```{r}
#| label: farm-ts-data

@@

# Species and population parameters

Load species-specific parameters from Excel file.

```{r}
#| label: species-parameters

@@

Load population-specific parameters.

```{r}
#| label: population-parameters

@@

@@

Calculations of expected harvest sizes for each farm (using default feed and no Monte-Carlo variation) are done in the targets pipeline.

```{r}
#| label: farm-harvest-size

Sys.setenv(TAR_PROJECT = "project_farmruns")
tar_prune() # will remove any targets objects no longer in pipeline

# Check that the feed will actually work
targets::tar_make(test_reference_feed)
targets::tar_load(test_reference_feed)
test_reference_feed # if weight ~ 0 then the feeds aren't processing properly

# Get harvest sizes for all farms
targets::tar_make(names = contains(c("harvest_size", "feed_params")))
targets::tar_load(harvest_size_chunked)
harvest_size <- harvest_size_chunked %>% bind_rows()

@@

Run the sensitivity runs using the targets pipeline. 
Note that this can take a long time. 
The species parameters (19) are run for a single fish in each farm (2721) and factor (3), which takes ~30 minutes. 
The population parameters (6) are run for a smaller number of farms (271) and each factor (3) with a simulated population of 500 fish, which takes ~30 hours.

```{r}
#| label: sensitivity-run

@@

targets::tar_validate()
# targets::tar_visnetwork(targets_only = T)
# targets::tar_outdated()

targets::tar_make(
  seconds_meta_append = 120,
  callr_function = NULL
  )
tar_prune()
```

@@

```{r}
#| label: sensitivity-results

targets::tar_load(sens_results_spec)
targets::tar_load(sens_results_pop)

@@

qs::qsave(sens_results, file.path(output_sens_data_path, paste0("sens_results_all.qs")))

@@

```{r}
#| label: run-farms-pipeline

@@

targets::tar_validate()
targets::tar_outdated()

# Pre-run to reduce load
targets::tar_make(
  names = c("farm_static_data_chunked", "farm_temp_data_chunked", "farm_ts_data_chunked"), 
  seconds_meta_append = 90
)

# Run results
targets::tar_make(
  names = c("farm_run_chunked", "farm_full_results"), 
  seconds_meta_append = 90,
  shortcut = T # only if you've done the pre-run, above
)

tar_prune()

# meta <- targets::tar_meta() %>% 
#   filter(grepl("farm_run", name))
# meta$seconds %>% mean()/60 # average minutes per target
```

@@

```{r}
#| label: all-farms-cohorts-results

targets::tar_load(stat_names)
targets::tar_load(farm_IDs_chunked)
farm_IDs_chunked <- farm_IDs_chunked %>% unlist()
targets::tar_load(feed_names)

print("Loading farm results...")
targets::tar_load(farm_results_chunked)
farm_results_chunked <- farm_results_chunked %>% 
  bind_rows()
for (stat_name in stat_names) {
  farm_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
}
rm(farm_results_chunked)

print("Loading cohort results...")
targets::tar_load(cohort_results_chunked)
cohort_results_chunked <- cohort_results_chunked %>% 
  bind_rows()
for (stat_name in stat_names) {
  cohort_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
}
rm(cohort_results_chunked)

targets::tar_load(biomass_produced_chunked)
qsave(biomass_produced_chunked, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
rm(biomass_produced_chunked)
```

```{r}

```

>>>>

```{r setup, include=F}
#| warning: false
#| message: false

@@

```{r filenames}
#| code-summary: Set up global filenames

@@

```{r farm-coordinates}
#| code-summary: Load and process farm coordinate data with appropriate timing parameters for Northern and Southern hemisphere farms

@@

```{r farm-sst-data}
#| label: farm-ts-data

@@

## Species and population parameters

```{r species-parameters}
#| code-summary: Load species-specific parameters from Excel file

@@

```{r population-parameters}
#| code-summary: Load population-specific parameters

@@

## Feed digestibility

```{r variable-digestibility}
#| code-summary: Show the variability in feed digestibility generated by sampling digestibility values.

# tar_make(names = c("feed_params", "feed_names"))

tar_load(feed_params)
tar_load(feed_names)

feed_params <- feed_params %>% 
  map2_dfr(., feed_names, function(fp, fn) {
    ld <- filter(fp[["Lipids"]], macro != 0)
    ld <- sum(ld$proportion * ld$digest)/sum(ld$proportion)

    cd <- filter(fp[["Carbohydrates"]], macro != 0)
    cd <- sum(cd$proportion * cd$digest)/sum(cd$proportion)

    pd <- filter(fp[["Proteins"]], macro != 0)
    pd <- sum(pd$proportion * pd$digest)/sum(pd$proportion)

    data.frame(
      protein_digestibility = pd,
      carb_digestibility = cd,
      lipid_digestibility = ld,
      feed_name = fn
    )
  }) %>% 
  pivot_longer(
    cols = contains("digestibility"),
    names_to = "macro", 
    values_to = "digestibility"
  ) %>% 
  mutate(
    macro = factor(
      macro, 
      levels = c("protein_digestibility", "lipid_digestibility", "carb_digestibility"),
      labels = c("protein", "lipid", "carb")
    ))

feed_params %>% 
  ggplot(aes(x = macro, y = digestibility, fill = feed_name)) +
  geom_col(position = position_dodge(), alpha = 0.35) +
  theme_classic()
```

@@

Calculations of expected harvest sizes for each farm (using default feed and no Monte-Carlo variation) are done in the targets pipeline. This also allows you to run some tests and make sure the pipeline is running correctly.

```{r check-farmrun-pipeline}
#| code-summary: Check that the pipeline will run correctly

Sys.setenv(TAR_PROJECT = "project_farmruns")
# tar_validate()
# tar_prune()

# tar_make(test_reference_feed)
tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly
```

```{r farm-harvest-size, eval=F}
#| code-summary: Run limited pipeline for harvest sizes and testing

# Get harvest sizes for all farms
tar_make(names = contains(c("harvest_size", "feed_params")))
```

```{r save-harvest-size}
#| code-summary: Save harvest size data

tar_load(harvest_size_chunked)
harvest_size <- bind_rows(harvest_size_chunked)

@@

Run the sensitivity runs using the targets pipeline - note that this can take a long time. The species parameters (n=19) are run for a single fish in  a sample number of farms (n=272) and each factor (3). The population parameters (n=6) are run for 1000 fish in a sample number of farms (271) and each factor (3).

```{r check-sensitivity-pipeline}
#| code-summary: Check that the sensitivities pipeline is running correctly

Sys.setenv(TAR_PROJECT = "project_sensitivities")
# tar_validate()
# tar_visnetwork(targets_only = T)

# tar_make(test_reference_feed)
tar_read(test_reference_feed) # if weight ~ 0 then feeds aren't processing properly, fix before proceeding
```

```{r sensitivity-run, eval=F}
#| code-summary: Run sensitivity pipeline

@@

tar_make(seconds_meta_append = 300)
tar_prune()
```

@@

```{r sensitivity-results}
#| code-summary: Plot and save sensitivity results

tar_load(sens_results_spec)
tar_load(sens_results_pop)

@@

qsave(sens_results, file.path(output_sens_data_path, paste0("sens_results_all.qs")))

@@

The following code runs the main pipeline in two stages. The pre-run prepares all the pre-requisites for the main results targets, to reduce load. The main run shortcuts past all the pre-run targets and does the main model runs and results processing.

```{r run-farms-pipeline, eval=F}
#| code-summary: Run the main pipeline

@@

# Pre-run to reduce load
tar_make(
  names = contains(c("data", "feed")),
  seconds_meta_append = 90
)

# tar_outdated()

# Run results
tar_make(
  names = c("farm_run_chunked", "farm_full_results"), 
  seconds_meta_append = 120,
  shortcut = T # only if you've done the pre-run, above
)
```

@@

```{r all-farms-cohorts-results}
#| code-summary: Save pipeline objects as files

tar_load(stat_names)
tar_load(farm_IDs_chunked)
farm_IDs_chunked <- farm_IDs_chunked %>% unlist()
tar_load(feed_names)

print("Loading farm results...")
tar_load(farm_results_chunked)
farm_results_chunked <- farm_results_chunked %>% 
  bind_rows()
for (stat_name in stat_names) {
  farm_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_farm_path, str_c(stat_name, "_all_farms.qs")))
}
rm(farm_results_chunked)

print("Loading cohort results...")
tar_load(cohort_results_chunked)
cohort_results_chunked <- cohort_results_chunked %>% 
  bind_rows()
for (stat_name in stat_names) {
  cohort_results_chunked %>% 
      filter(measure == stat_name) %>% 
      qsave(file.path(output_model_cohort_path, str_c(stat_name, "_all_farms.qs")))
}
rm(cohort_results_chunked)

tar_load(biomass_produced_chunked)
qsave(biomass_produced_chunked, file.path(output_model_farm_path, str_c("biomass_produced_all_farms.qs")))
rm(biomass_produced_chunked)
```

### 2025-12-11 docs-working/07_methods_and_supplementaries/_manuscript/05_methods_and_supplementaries.qmd
Moving files around

source(here("00_model_functions.R"))

# Sys.setenv(TAR_PROJECT = "project_main")
indi_store <- here() %>% file.path("04_targets_individual")
farm_IDs <- tar_read(farm_IDs, store = indi_store)
b1 <- sample(length(farm_IDs), 100, replace = F)
b2 <- b1 + length(farm_IDs)
b3 <- b2 + length(farm_IDs)
b <- c(b1, b2, b3)
```

@@

@@

# This is the full idealised year (2 years?) of temperature data
sst <- here() %>% file.path("data", "_general_data", "SST", "farm_SST_extracted.parquet") %>% read_parquet()

# This is the actual temperature curve for the farming period
farm_temp <- tar_read(example_individual, store = indi_store, branches = b1)
```

@@

species_params <- tar_read(species_params, store = indi_store)
pop_params <- tar_read(pop_params, store = indi_store)
weight <- tar_read(example_individual, store = indi_store, branches = b) %>% select(farm_ID, weight, days, prod_days, feed)
SGR <- tar_read(example_individual, store = indi_store, branches = b) %>% select(farm_ID, SGR, days, prod_days, feed)
FCR <- tar_read(example_individual, store = indi_store, branches = b) %>% select(farm_ID, FCR, days, prod_days, feed)

@@

df <- data.frame(water_temp = seq(0, 30, 0.25))
df$resp <- exp(species_params['pk']*df$water_temp)

@@

feed_params_protein <- tar_read(feed_params_protein, store = indi_store)
feed_params_carbs <- tar_read(feed_params_carbs, store = indi_store)
feed_params_lipids <- tar_read(feed_params_lipids, store = indi_store)
```

@@

#c(b1, b2, b3))
ing_pot <- tar_read(example_individual, store = indi_store, branches = b1) %>% select(farm_ID, ing_pot, days, prod_days, feed)
ing_act <- tar_read(example_individual, store = indi_store, branches = b1) %>% select(farm_ID, ing_act, days, prod_days, feed)
food_prov <- tar_read(example_individual, store = indi_store, branches = b1) %>% select(farm_ID, food_prov, days, prod_days, feed)
```

@@

params <- tar_read(sens_all_params, store = indi_store)
pnames <- names(params)
```

>>>>

source(here("src/spatial_templates.R"))
source(here("src/model_functions.R"))

# Sys.setenv(TAR_PROJECT = "project_main")
base_path <- file.path("C:", "Users", "treimer", "Documents", "R-temp-files", "local_to_global_mariculture_modelling")
targets_store <- file.path(base_path, "targets", "_targets_individual")
farm_IDs <- tar_read(farm_IDs, store = targets_store)
b1 <- sample(length(farm_IDs), 100, replace = F)
b2 <- b1 + length(farm_IDs)
b3 <- b2 + length(farm_IDs)
b <- c(b1, b2, b3)
```

@@

We adapted the methods of @baldan_r_2018 to create a bioenergetic model that simulates individual growth and farm-scale production for Atlantic salmon and the resultant nutrient waste in the form of excess labile nitrogen and phosphorus. 
The model simulates growth at an individual level, calculating the change in individual weight through time using:

$$
\frac{dw}{dt} = \frac{A-C}{\epsilon}
$$

Where $w=$ is wet weight (t), $t=$ time (d), $A=$ anabolic rate (J t$^{-1}$), $C=$ the catabolic rate (J t$^{-1}$), $\epsilon=$ energy density of body tissues (J t$^{-1}$).

Individual models were then upscaled using monte-carlo simulations to simulate size structure in a population. Size differences were achieved through different initial starting weights and ingestion rates for different finfish species. All individuals have a fixed mortality rate to simulate stocking and harvesting.

* Parameterised for atlantic salmon
* Farms with mean temperature < 8.5$^\circ$ were excluded

@@

# This is the full idealised year (2 years?) of temperature data
sst <- file.path(base_path, "data", "_general_data", "SST", "farm_SST_extracted.parquet") %>% read_parquet()

# This is the actual temperature curve for the farming period
farm_temp <- tar_read(example_individual, store = targets_store, branches = b1)
```

@@

species_params <- tar_read(species_params, store = targets_store)
pop_params <- tar_read(pop_params, store = targets_store)
weight <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, weight, days, prod_days, feed)
SGR <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, SGR, days, prod_days, feed)
FCR <- tar_read(example_individual, store = targets_store, branches = b) %>% select(farm_ID, FCR, days, prod_days, feed)

@@

df <- data.frame(water_temp = seq(-5, 30, 0.25))
df$resp <- exp(species_params['pk']*df$water_temp)

@@

feed_params_protein <- tar_read(feed_params_protein, store = targets_store)
feed_params_carbs <- tar_read(feed_params_carbs, store = targets_store)
feed_params_lipids <- tar_read(feed_params_lipids, store = targets_store)
```

@@

#c(b1, b2, b3))
ing_pot <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, ing_pot, days, prod_days, feed)
ing_act <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, ing_act, days, prod_days, feed)
food_prov <- tar_read(example_individual, store = targets_store, branches = b1) %>% select(farm_ID, food_prov, days, prod_days, feed)
```

@@

params <- tar_read(sens_all_params, store = targets_store)
pnames <- names(params)
```

### 2025-12-11 docs-working/index.qmd
Moving files around

---
title: "Local to Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true # quarto render index.qmd --cache-refresh
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
format:
  html:
    code-fold: true
---

@@

All code and processes for this project are linked below. Note that some scripts require access to raw data which is not stored on Github. 
While this page (the index) has code that runs prior to rendering, all code in the subsequent pages has not been run for rendering.

>>>>

---
title: "Local-to-Global Mariculture Modelling"
subtitle: "Project Documentation"
author: "Dr Tormey Reimer"
date: today
execute:
  eval: true
  echo: false
  warning: false
  message: false
  cache: true # quarto render index.qmd --cache-refresh
knitr: 
  opts_chunk:
    fig.align: center
    fig.width: 8.5
format:
  html:
    code-fold: true
---

@@

All code and processes for this project are linked below. Note that some scripts require access to raw data which is not stored on Github.
